Manuscript draft

### 2019-09-10 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

*Length of growing season.* Growing season months were defined as months with mean minimum temperature > 0.5. Growing season months were initially calculated following methods used by Kerkhoff et al. (2005), which additionally required that growing season months had a moisture index, defined as (MAT - PET)/PET, > -0.95. Michaletz et al. (2014) included an equivalent requirement in their calculation of growing season length. However, we found that including this requirement had no effect on the estimates of growing season length, and so chose to exclude it.

@@

>>>>

*Length of growing season.* Growing season months were defined as months with mean minimum temperature > 0.5$^\circ$C. Growing season months were initially calculated following methods used by Kerkhoff et al. (2005), which additionally required that growing season months had a moisture index, defined as (MAT - PET)/PET, > -0.95. Michaletz et al. (2014) included an equivalent requirement in their calculation of growing season length. However, we found that including this requirement had no effect on the estimates of growing season length, and so chose to exclude it.

@@

### Supporting Information

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/S1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, booktabs = TRUE, caption = "Hypothesis table", escape = F)
```
